XXXXX \todo{Le titre !} XXXXX

### 2013-03-22 parts/def-ph.tex
defs + proof

@@

\paragraph{Components \& cooperative sorts}
The studied PH is only composed of sorts representing regular components with priority $2$ and of cooperative sorts with priority $1$.

@@

>>>>

Sorte coopérative :
$a$ is a well-formed cooperative sort iff:
\begin{itemize}
  \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 1$
  \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, |\pfp_s(a)| = 1$
\end{itemize}

Composant :
$a$ is a well-formed component iff:
\begin{itemize}
  \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2$
\end{itemize}

We call $\components$ the set of well-formed components and $\cs$ the set of well-formed cooperative sorts.
We note that: $\forall a \in \components, \Vs(a) = \emptyset \wedge \Vh(a) = \emptyset$

@@

\paragraph{Components \& cooperative sorts}
The studied PH is a PH with 2 priorities, and it is only composed of well-formed components and cooperative sorts:
$\components \cup \cs = \PHs \wedge \components \cap \cs = \emptyset$

\paragraph{Bounded termination}
The dynamics of model $\restriction{\PH}{1}$ contains no cycles. Cycles are still allowed in $\PH$ however.
Formally : $\exists N \in \sN, \forall \delta \in \restriction{\Sce}{1}, |\indexes{\delta}| \leq N$.

@@

\subsection{Consequences of the restrictions}
\pref{th:hcompcomp} states that for a given state $s$ and for any action $h = \PHhit{a_i}{b_j}{b_k}$ between well-formed components, $h$ can be played after a series of hits that do not prevent it to be fired.
\pref{th:hcscomp} states the same if $a$ is a well-formed cooperative sort, under the condition that $a_i$ reflects the state of the neighborhood of $a$.
\begin{theorem}
\label{th:hcompcomp}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a,b \in \components,$\\
  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}, \text{$h$ can be played in $s \PHplay \delta$})$
\end{theorem}
\begin{proof}
  There exists a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
  As $a,b \in \components$, $a_i \in s \PHplay \delta$ and $b_j \in s \PHplay \delta$.
  Finally, by definition of $\update(s)$, no action of priority $1$ can be played in $s \PHplay \delta$, thus $h$ can be played in $s \PHplay \delta$.
\end{proof}
\begin{theorem}
\label{th:hcscomp}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a \in \cs, b \in \components$\\
  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge \pfp_s(a) = a_i) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}, \text{$h$ can be played in $s \PHplay \delta$})$
\end{theorem}
\begin{proof}
  There exists a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
  As $a_i \in \pfp_s(a)$, $a_i \in s \PHplay \delta$.
  Furthermore, $b \in \components$, thus $b_j \in s \PHplay \delta$.
  Finally, by definition of $\update(s)$, no action of priority $1$ can be played in $s \PHplay \delta$, thus $h$ can be played in $s \PHplay \delta$.
\end{proof}

\pref{th:autohits} states that any sequence $\zeta$ of self-actions on a well-formed component can be played eventually.
\begin{theorem}
\label{th:autohits}
  Let $a \in \PHs$, $s \in \PHl$ and $\zeta \in \BS$ so that $\forall i \in \indexes{\zeta}, \PHsort(\PHhitter(\zeta_i)) = \PHsort(\PHtarget(\zeta_i)) = a$.
  $\exists (\delta_i)_{i \in \indexes{\zeta}} \in \restriction{\Sce}{1}$ so that $\forall i \in \indexes{\zeta}$, $\zeta_i$ can be played in $s \PHplay \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_i$. 
\end{theorem}
\begin{proof}
  With \pref{th:hcompcomp} applied iteratively.
\end{proof}

### 2013-03-22 parts/sa.tex
defs + proof

@@

\begin{definition}
  \label{def:aS}
  The abstract structure $\cwB=(\Breq,\Bsol,\Bcont,\Bsat)$ is defined as
  $
  \cwB = \sfp{\myB}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}
  $,
  with $\myB=(\myreq,\mysol,\mycont,\mysat)$:
  \begin{align*}
    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
      a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
      & \qquad \wedge (\exists (P,ps) \in \mysol, a_i \in ps \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
    \\
    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
      & \qquad\qquad \vee \exists (Q, P) \in \mycont \wedge ps \in \aBS(P) \}
    \\
    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
      \exists (P, ps) \in \mysol \\
      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
    \\
    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
      a_j \neq a_k \wedge a_k \in \pfp_\ctx(a) \}
%%% Version états stables locaux
%    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
%      \exists (a_i, \PHobjp{a}{j}{i}) \in \myreq, \\
%      & \qquad\qquad a_j \neq a_k \wedge a_k \in \pfpprocs_\ctx(a) \\
%      & \qquad\qquad \wedge (\exists (P, ps) \in \mysol, a_i \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
%      & \qquad\qquad\qquad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \mysol, \exists p \in ps, \exists (p, P) \in \myreq,\\
%      & \qquad\qquad\qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
  \end{align*}
\end{definition}

@@

\begin{proof}
\todo{À refaire}

\begin{comment}
We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
for all objective $P$ in $\cwB$ so that $\PHtarget(P) \in s$,
$\exists \delta \in \muconcr_s(P)$.% and $\ceil(\delta) \subseteq max\ctx$.

@@

  \item Suppose all children objectives of $P$ are concretizable.
  \begin{itemize}
    \item If $\exists Q \in \Bcont$, then by hypothesis,
      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
      $\muconcr_{s}(P) \neq \emptyset$.
    \item Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bsol$.
      We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
%      \todo{Idée avec les nouvelles defs : au rang 0, on se replace sur un processus de $\pfp$. Au rang n, il existe par saturation un objectif adéquat qui “reprend” la progression.}
      \begin{itemize}
%        \item[*] Let $\zeta_1 = \PHhit{b_i}{a_j}{a_k}$. By hypothesis, $\exists \delta_1 \in \muconcr_s(\PHobj{\any}{b_i}), \PHget{s \PHplay \delta_1}{a} \in \pfp_s(a)$.
%          If $\PHget{s \PHplay \delta_1}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s \PHplay \delta_1}{a}}{a_k}) \in \Bsat$.
%          By hypothesis, $\muconcr_s(\PHobj{\any}{a_k}) \neq \emptyset$.
%          If $\PHget{s \PHplay \delta_1}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_1 \in \Sce$, $\zeta_1$ can be played in $s \PHplay \delta_1 \PHplay \delta'_1$.
        \item[*] For $n \in \indexes{\zeta}$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{n-1} \PHplay \delta'_{n-1} \PHplay \zeta_{n-1}$ (or $s_1 = s$),
          and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$. By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$, and we have: $\PHget{s_n \PHplay \delta_n}{a} \in \bounceprocs_{s_n} \subset \bounceprocs_\ctx$ \todo{À montrer}.
          If $\PHget{s_n \PHplay \delta_n}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s_n \PHplay \delta_n}{a}}{a_k}) \in \Bsat$.
          By hypothesis, $\muconcr_{s_n \PHplay \delta_n}(\PHobj{\any}{a_k}) \neq \emptyset$.
          If $\PHget{s_n \PHplay \delta_n}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_n \in \restriction{\Sce}{k-1}$, $\zeta_n$ can be played in $s \PHplay \delta_n \PHplay \delta'_n$
          \todo{$\delta'_n$ ne perturbe pas $b$ ?}
          .
%        \item[*] For $n \in \segm{1}{m-1}$, $m = |\indexes{\zeta}|$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_n \PHplay \delta'_n \PHplay \zeta_n$ and $\zeta_{n+1} = \PHhit{c_i}{a_j}{a_k}$.
%          By hypothesis, $\exists \delta_1 \in \muconcr_{s_n}(\PHobj{\any}{c_i}), \PHget{s_n \PHplay \delta_{n+1}}{a} \in \pfp_s(a)$.
      \end{itemize}
      Thus, $\delta = \delta_m \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
  \end{itemize}
\end{itemize}

Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (property \towrite{xxx}).
\end{comment}
\end{proof}

>>>>

Mise à jour de l'état initial :
\begin{align*}
  \update(\ctx) = \ctx \Cap \bigcup_{a \in CS} \pfp_{\restriction{\ctx}{\Vs(a) \cup \{ a \}}}(a)
\end{align*}

@@

\begin{definition}
  \label{def:aS}
  The abstract structure $\cwB=(\Breq,\Bsol,\Bcont,\Bsat)$ is defined as
  $\cwB = \sfp{\aB^\w_{\update(\ctx)}}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,\\
  with $\myB=(\myreq,\mysol,\mycont,\mysat)$:
  \begin{align*}
    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
      a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
      & \qquad \wedge (\exists (P,ps) \in \mysol, a_i \in ps \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
    \\
    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
      & \qquad\qquad \vee \exists (Q, P) \in \mycont \wedge ps \in \aBS(P) \}
    \\
    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
      \exists (P, ps) \in \mysol \\
      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
    \\
    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
      a_j \neq a_k \wedge a_k \in \pfp_\ctx(a) \}
%%% Version états stables locaux
%    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
%      \exists (a_i, \PHobjp{a}{j}{i}) \in \myreq, \\
%      & \qquad\qquad a_j \neq a_k \wedge a_k \in \pfpprocs_\ctx(a) \\
%      & \qquad\qquad \wedge (\exists (P, ps) \in \mysol, a_i \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
%      & \qquad\qquad\qquad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \mysol, \exists p \in ps, \exists (p, P) \in \myreq,\\
%      & \qquad\qquad\qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
  \end{align*}
\end{definition}

@@

\begin{proof}
We note $max\ctx = \update(\ctx) \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
for all objective $P$ in $\cwB$ so that $\PHtarget(P) \in s$,
$\exists \delta \in \muconcr_s(P)$.% and $\ceil(\delta) \subseteq max\ctx$.

@@

  \item Suppose all children objectives of $P$ are concretizable.
  \begin{itemize}
    \item If $\exists Q \in \Bcont$, then by hypothesis,
      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
      $\muconcr_{s}(P) \neq \emptyset$.
    \item Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bsol$.
      We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
%      \todo{Idée avec les nouvelles defs : au rang 0, on se replace sur un processus de $\pfp$. Au rang n, il existe par saturation un objectif adéquat qui “reprend” la progression.}
      \begin{itemize}
%        \item[*] Let $\zeta_1 = \PHhit{b_i}{a_j}{a_k}$. By hypothesis, $\exists \delta_1 \in \muconcr_s(\PHobj{\any}{b_i}), \PHget{s \PHplay \delta_1}{a} \in \pfp_s(a)$.
%          If $\PHget{s \PHplay \delta_1}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s \PHplay \delta_1}{a}}{a_k}) \in \Bsat$.
%          By hypothesis, $\muconcr_s(\PHobj{\any}{a_k}) \neq \emptyset$.
%          If $\PHget{s \PHplay \delta_1}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_1 \in \Sce$, $\zeta_1$ can be played in $s \PHplay \delta_1 \PHplay \delta'_1$.
        \item[*] For $n \in \indexes{\zeta}$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{n-1} \PHplay \delta'_{n-1} \PHplay \zeta_{n-1}$ (or $s_1 = s$),
          and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
          By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$.
          If $a \in \cs$, then $\prio(\zeta_n) = 1$ and $\zeta_n$ can be played in $s_n \PHplay \delta_n$ (\ie $\delta'_n = \varepsilon$).
          If $a \notin \cs$ and $b \in \cs$, then there exists a scenario $\widehat{\delta_n}$ so that $b_i \in \pfp_{s_n \PHplay \delta_n \PHplay \widehat{\delta_n}}(b)$.
          Then, by \pref{th:hcscomp}, there is a scenario $\delta' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \widehat{\delta_n} \PHplay \delta'_n$.
          Finally, if $a,b \in \components$, then by \pref{th:hcompcomp}, there is a scenario $\delta' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta'_n$.
      \end{itemize}
      Thus, $\delta = \delta_m \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
  \end{itemize}
\end{itemize}

Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (property \towrite{xxx}).
\end{proof}
